parallel for the env. data grab

### 2018-12-03 src/parallel_env_data.Rmd
not working

```{r}
test_back <- read.csv("../data/looptest.csv", header = TRUE) #test dataset

```

@@

```{r}
strt <- Sys.time() #get the start time
netcdf_list <- list.files("../data/testloopnetcdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
for (i in 1:no_netcdf) {  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  brkvar <- (sapply(strsplit(netcdf_name[i], "_"), "[[", 3)) # extracting the third part of the netcdf (inc.nc)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:nrow(test_back)) {  
      de <- test_back$depthlayerno[[j]]  # a variable for the observation depth layer
      yr <- (test_back$year[j])  # a variable for the observation year
      mth <- (test_back$month[j])  # a variable for the observation month
          if (brkyr == yr & brkmth == mth & brkvar == "temp.nc"){
              test_back$temp_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$temp_depth[j] <- NA
              } else  
                test_back$temp_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "salinity.nc") {
              test_back$salinity_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$salinity_depth[j] <- NA
              } else  
                test_back$salinity_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "chl.nc") {
              test_back$chl_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$chl_depth[j] <- NA
              } else  
                test_back$chl_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "o2.nc") {
              test_back$o2_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$o2_depth[j] <- NA
              } else  
                test_back$o2_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "mlp.nc") {
              test_back$mlp_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "ssh.nc") {
              test_back$ssh_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ])

@@

>>>>

```{r}
test_back_or <- read.csv("../data/looptest.csv", header = TRUE) #test dataset
xy <- test_back_or[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude
test_back <- SpatialPointsDataFrame(coords = xy, data = test_back_or, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.
```

@@

```{r}
strt <- Sys.time() #get the start time
netcdf_list <- list.files("../data/testloopnetcdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/testloopnetcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
for (i in 1:no_netcdf) {  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  brkvar <- (sapply(strsplit(netcdf_name[i], "_"), "[[", 3)) # extracting the third part of the netcdf (inc.nc)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:nrow(test_back)) {  
      de <- test_back$depthlayerno[[j]]  # a variable for the observation depth layer
      yr <- (test_back$year[j])  # a variable for the observation year
      mth <- (test_back$month[j])  # a variable for the observation month
          if (brkyr == yr & brkmth == mth & brkvar == "temp.nc"){
              test_back$temp_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$temp_depth[j] <- NA
              } else  
                test_back$temp_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "salinity.nc") {
              test_back$salinity_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$salinity_depth[j] <- NA
              } else  
                test_back$salinity_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "chl.nc") {
              test_back$chl_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$chl_depth[j] <- NA
              } else  
                test_back$chl_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "o2.nc") {
              test_back$o2_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$o2_depth[j] <- NA
              } else  
                test_back$o2_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "mlp.nc") {
              test_back$mlp_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "ssh.nc") {
              test_back$ssh_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ])

@@

# edit test 1

```{r}
test_back_or <- read.csv("../data/looptest.csv", header = TRUE) #test dataset
xy <- test_back_or[ ,c("longitude_meters","latitude_meters")] # This is to tell R where the coordinates are. Note that the column order needs to be longitude, latitude
test_back <- SpatialPointsDataFrame(coords = xy, data = test_back_or, proj4string = CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-60 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs")) # The CRS is used here is for the albers equal area projection.

ncores <- detectCores()
cl <- (ncores)-1
registerDoParallel(cl)

strt <- Sys.time() #get the start time

netcdf_list <- list.files("../data/testloopnetcdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/testloopnetcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
aea <- raster("../output/env/aea.tif") 
foreach ((i = 1:no_netcdf) , .packages = "raster") %dopar% {  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  brkvar <- (sapply(strsplit(netcdf_name[i], "_"), "[[", 3)) # extracting the third part of the netcdf (inc.nc)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    foreach (j = 1:nrow(test_back)) %dopar% {  
      de <- test_back$depthlayerno[[j]]  # a variable for the observation depth layer
      yr <- (test_back$year[j])  # a variable for the observation year
      mth <- (test_back$month[j])  # a variable for the observation month
          if (brkyr == yr & brkmth == mth & brkvar == "temp.nc"){
              test_back$temp_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$temp_depth[j] <- NA
              } else  
                test_back$temp_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "salinity.nc") {
              test_back$salinity_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$salinity_depth[j] <- NA
              } else  
                test_back$salinity_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "chl.nc") {
              test_back$chl_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$chl_depth[j] <- NA
              } else  
                test_back$chl_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "o2.nc") {
              test_back$o2_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ]) 
              if (is.na(de)){
                test_back$o2_depth[j] <- NA
              } else  
                test_back$o2_depth[j] <- extract(x=temp_brick[[de]], y = test_back[j, ]) 
          } else if (brkyr == yr & brkmth == mth & brkvar == "mlp.nc") {
              test_back$mlp_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ])
          } else if (brkyr == yr & brkmth == mth & brkvar == "ssh.nc") {
              test_back$ssh_surface[j] <- extract(x=temp_brick[[1]], y = test_back[j, ])

    }
}
write.csv(test_back, "../data/testloopoutput.csv", row.names = FALSE)
test_back_df <- as.data.frame(test_back)
head(test_back_df)
stopCluster(cl)
print(Sys.time()-strt) #time it took to run
```
